Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''

### 2019-05-20 tex/v3/section_5_numeric_expes.tex

\begin{figure*}[t]
	\centering
%	\includegraphics[width=4.cm]{../../figure/wda_accur_toy.pdf}
%	\includegraphics[width=4.cm]{../../figure/wda_accur_mnist.pdf}
	\includegraphics[width=6.cm]{../../figure/wda_gain_toy.pdf}
\includegraphics[width=6.cm]{../../figure/wda_gain_mnist.pdf}
	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:wda}
\end{figure*}
\begin{figure*}[t]
	\centering

	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_mnist_regcl10.pdf}
	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
%	\includegraphics[width=4.cm]{./figs/wda_accur_toy.pdf}
%	\includegraphics[width=4.cm]{../figs/wda_accur_mnist.pdf}
	\includegraphics[width=6.cm]{./figs/wda_gain_toy.pdf}
\includegraphics[width=6.cm]{./figs/wda_gain_mnist.pdf}
	\caption{Wasserstein Discriminant Analysis : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:wda}
\end{figure*}
\begin{figure*}[t]
	\centering

	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl1.pdf}
	\includegraphics[width=6.cm]{./figs/da_gain_mnist_regcl10.pdf}
	\caption{OT Domain adaptation : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}
